\scuba: iterative map-making with the Sub-Millimetre User Reduction Facility

### 2012-11-16 smurf_paper.tex
added some flagging statistics as requested by referee

Prior to executing the iterative part of the algorithm, the data must
undergo several pre-processing steps. First, the data files are read
into memory and concatenated into continuous arrays (\scuba\ data are
broken up and written to disk every $\sim$30\,s regardless of the
observation length during data acquisition). As the data are loaded,
they are multiplied by the flatfield correction \citep[see Section~2.1
in][]{dempsey2012}. Next, a series of configurable data cleaning and
filtering procedures are applied; these include the removal of large
glitches that may hinder the iterative solution from converging, or
simply tasks that do not need to be iterated.

@@

\subsubsection{Additional bad bolometer rejection}
\label{sec:flagbadbol}

Despite the cleaning operations described in the previous sections,
the data from a given bolometer may be unusable due to it being poorly
biased, having an incorrect flatfield correction applied, or having
some other particularly pathological noise contamination. Most of
these bolometers can be flagged simply by identifying outliers in the
distribution of bolometer white noise levels. By default, SMURF
measures the PSD of all bolometers between 2 and 10\,Hz, after all
other pre-processing steps have been run (identical to the measurement
in Section~\ref{sec:noi}). Despite having significant low-frequency
noise (and possibly bright astronomical source) contamination, this
higher-frequency portion of the PSD is generally quite
clean. Furthermore, even if there is contamination, the purpose of
this measurement is to identify outliers, rather than provide a
meaningful absolute measurement of a given bolometer's white noise
level. Both high and low (e.g., due to an incorrect and very small
flatfield correction being applied) outliers from the centre of the
logarithm (to reduce the impact of outliers) of the bolometer noise
distribution are flagged.

@@

>>>>

Prior to executing the iterative part of the algorithm, the data must
undergo several pre-processing steps. First, the data files are read
into memory and concatenated into continuous arrays (\scuba\ data are
broken up and written to disk every $\sim$30\,s regardless of the
observation length during data acquisition). As the data are loaded,
they are multiplied by the flatfield correction \citep[see Section~2.1
in][]{dempsey2012}. Next, a series of configurable data cleaning and
filtering procedures are applied; these include the removal of large
glitches that may hinder the iterative solution from converging, or
simply tasks that do not need to be iterated. All of the data that are
flagged as bad are ignored when estimating the map. As an example, for
the 450\,\micron\ scan of Uranus that will be presented in
Section~\ref{sec:point}: 31.00\% of the data (1587/5120 bolometers)
are flagged due to data acquisition problems (dead or deactivated
bolometers, or non-linear flatfields); 0.12\% of the data are flagged
due to steps (including a small region about the steps); and 0.83\% if
the data are flagged because the telescope was stationary.

@@

\subsubsection{Additional data rejection}
\label{sec:flagbadbol}

Despite the cleaning operations described in the previous sections,
the data from a given bolometer may be unusable due to it being poorly
biased, having an incorrect flatfield correction applied, or having
some other particularly pathological noise contamination. Most of
these bolometers can be flagged simply by identifying outliers in the
distribution of bolometer white noise levels. By default, SMURF
measures the PSD of all bolometers between 2 and 10\,Hz, after all
other pre-processing steps have been run (identical to the measurement
in Section~\ref{sec:noi}). Despite having significant low-frequency
noise (and possibly bright astronomical source) contamination, this
higher-frequency portion of the PSD is generally quite
flat. Furthermore, even if there is contamination, the purpose of this
measurement is to identify outliers, rather than provide a meaningful
absolute measurement of a given bolometer's white noise level. Both
high and low (e.g., due to an incorrect and very small flatfield
correction being applied) outliers from the centre of the logarithm
(to reduce the impact of outliers) of the bolometer noise distribution
are flagged.

Finally, data that are taken while the telescope is either moving
extremely slowly, or extremely fast, are flagged and ignored when
estimating the map. When the telescope is moving slowly, astronomical
signals appear at low frequencies in the bolometer data that are
dominated by $1/f$ noise (in the extreme case of no motion, the
bolometers have zero sensitivity). When the telescope is moving
significantly faster than 600\,arcsec\,s$^{-1}$, both the thermal
response of the bolometers, and the anti-aliasing filter in the
readout electronics (Section~\ref{sec:bolos}) can significantly
distort signals.  The default allowable range of speed is
30--1000\,arcsec\,s$^{-1}$, which primarily rejects short periods when
the telescope was stationary prior to commencing the scan pattern
(generally speaking the speed is constant once the scan begins),
although the scan speed can briefly exceed the upper limit, even for a
requested speed of 600\,arcsec, if the pointing system is having
trouble keeping-up for large-area scans at high elevation.

@@

Additional flagging of data to be ignored in the map occurs during the
iterations. For the example of the 450\,\micron\ Uranus scan in
Section~\ref{sec:point}: an additional 55 spikes are detected using
the map-based despiker ($1.2\times10^{-6}$ \% of the data); and 0.72\%
of the data are flagged as outliers compared to the common-mode.
